\section{Control Model and Input}
From parameter estimates (Table~\ref{tab::parm_ests}), it can be seen that the
estimate of total 'damping' factor $( b_m )$ is zero. Thus, the linear term of
the control input in the RHS of eqn.~\ref{eqn::nl_model} can be ignored.
Let $u = u_\omega ^2 $ be the control input to the system for which we are going
to design the feedback controller. Incorporating the above two assumptions into
eqn.~\ref{eqn::nl_model}, we have the control form of the model:
\begin{equation} \label{eqn::control_form}
    J \dot \omega + b_m \omega + C_D \omega^2 + M_f \delta v = V_{in}^2 (1 + \delta v) C_D u
\end{equation}

We have the following bounds on the control input:
\begin{align*}
    u &= u_\omega^2 = \lr{a u_p + b}^2\\
    \implies u_{min} &= \lr{a u_{p_{min}}  + b}^2 = \lr{0.0696 \times 1110 - 64.3266}^2 = 167.1694\\
    \implies u_{max} &= \lr{a u_{p_{max}}  + b}^2 = \lr{0.0696 \times 1890 - 64.3266}^2 = 4518.1789\\
\end{align*}

The goal of feedback control design for the actuator is two-fold:
\begin{enumerate}
\item Compensate for the input-uncertainities, un-modelled disturbances and
model-structure errors.
\item Make the actuator track the response of a second-order transfer function
with no over-shoot of the form:
\begin{align*}
    G_{ref}(s) &= \frac{1}{s^2 + 2 \zeta \omega_{ref} + \omega_{ref}^2}
    && \zeta = \frac{1}{\sqrt{2}} = 0.707
\end{align*}
Such that, $\omega_{ref}$ results in the maximum possible bandwidth in presence
of uncertainties mentioned above.
\end{enumerate}

To this end, two feedback control designs based on Adaptive Robust Control
Theory (ARC) are implemented, and their performances are compared:
\begin{enumerate}
    \item Direct/Indirect Adaptive Robust Controller (DIARC).
    \item ARC design with parameter estimation only for the disturbances(Disturbance ARC).
    \item Feedback linearization.
\end{enumerate}

%===============================================================================
\subsection{Parametric model and parameter bounds for ARC design}

The parameter bounds are obtained from the variance of estimates and the
maximum value of $\delta v$. For the current design $\pm 2\sigma$ bounds are
used for each of the $\theta$'s. From experimental observations, the maximum
supply voltage is about $16\, V$ and minimum supply voltage is close to $15\,
V$. The average would be in the middle ($15.5\, V$). The physics dictates that
all the physical parameters have a non-negative value. Also, the minimum value
of $J$ is assumed to be $1/10$ of its nominal value instead of zero. This is to
ensure that the inertia estimate would never be zero and with-in the reasonable
limits. The following table gives the minimum, maximum and nominal values of the parameters:

\begin{table}[H]
    \centering
    \begin{tabular}{r l r r r}
        \hline \hline
        Parameter & Units &Nominal & Minimum & Maximum \\ \hline \hline
        $C_T$                   &
        $N/(rad/s)^2$           &
        $7.2581e-6$             &
        $7.1690e-6$             &
        $7.3471e-6$
        \\
        $C_D$                   &
        $N.m/(rad/s)^2$         &
        $3.6088e-8$             &
        $3.3295e-8$             &
        $3.8881e-8$

        \\
        $b_m$                    &
        $N.m/(rad/s)$            &
        $0$                      &
        $0$                      &
        $9.2006e-6$
        \\
        $M_f$                    &
        $N.m$                    &
        $1.3135e{-3}$            &
        $0$                      &
        $0.0104$
        \\
        $J$                      &
        $Kg.m^2$                 &
        $3.2238e{-6}$            &
        $3.2238e{-7}$            &
        $1.7234e-5$
        \\
        $V_{in}$                 &
        $V$                      &
        $15.5$                   &
        $15$                     &
        $16$
        \\
        $\delta v$               &
                                 &
        $0$                      &
        $-0.2$                   &
        $0.2$
        \\
        \hline \hline
    \end{tabular}
    \caption{Summary of parameter bounds}
    \label{tab::parm_bounds}
\end{table}

\subsubsection{Parametric Model}
It can be noted that the variance of $\hat J$ is substantial as compared to its
actual value. This would propagate into the all the parameters if it is divided
on all sides. Instead, we normalize all the coefficients with the controller
gain to minimize the propagation of variance to the parameters. Thus,
eqn.~\ref{eqn::control_form} becomes:

\begin{align*}
    \lr{\frac{J}{V_{in}^2 C_D}} \dot \omega + \lr{\frac{b_m}{V_{in}^2 C_D}} \omega + \lr{\frac{1}{V_{in}^2}} \omega^2  &= u + \delta v \lr{u - \frac{M_f}{V_{in}^2 C_D}}\\
    %===
    \text{Let, } \qquad &\\
    \theta_1 = \lr{\frac{J}{V_{in}^2 C_D}} \qquad
    \theta_2 &= \lr{\frac{b_m}{V_{in}^2 C_D}}\qquad
    \theta_3 = \lr{\frac{1}{V_{in}^2}}\\
    d(t) &= \delta v \lr{u - \frac{M_f}{V_{in}^2 C_D}}\\
    %===
    \implies \theta_1 \dot \omega + \theta_2 \omega + \theta_3 \omega^2 &= u + d(t)
\end{align*}
\begin{equation}\label{eqn::almst_ctrl_mdl}
    \theta_1 \dot \omega = u - \theta_2 \omega - \theta_3 \omega^2 + d(t)
\end{equation}

Let, $\omega_d(t)$ be the desired trajectory that the system needs to track
(output of $G_{ref}(s)$). Thus, the tracking error:
\begin{align*}
    s &= \omega - \omega_d \quad \implies \dot s = \dot \omega - \dot \omega_d
\end{align*}
Dividing the disturbance into high-frequency component and a slowly varying
component, let, $$d(t) = d_0 + \Delta(t)$$
Thus, subtracting $\theta_1 \omega_d$ on both sides of eqn.~\ref{eqn::almst_ctrl_mdl}.
\begin{align*}
    \theta_1 (\dot \omega - \dot \omega_d) &= u - \theta_1 \omega_d - \theta_2 \omega - \theta_3 \omega^2 + d_0 + \Delta(t)\\
    \text{Let,} \qquad\\
    \pmb \theta &= \bm{\theta_1 & \theta_2 & \theta_3 & d_0}^T\\
    \pmb \phi &= \bm{-\omega_d & -\omega & - \omega^2 & 1}^T\\
\end{align*}
Thus we have the model for tracking error dynamics:
\begin{equation}\label{eqn::error_dyn}
    \theta_1 \dot s = u + \pmb \phi^T \pmb \theta + \Delta(t)
\end{equation}


\subsubsection{Parameter Bounds}
The parameter bounds for eqn.~\ref{eqn::error_dyn} are obtained from the
parameter bounds of estimated parameters. Also,
\begin{align*}
    \abs{d(t)} &\leq d_M \implies \abs{d_0} \leq d_M \text{  and  } \abs{\Delta} \leq 2d_M = \Delta_M\\
    \text{From Table~\ref{tab::parm_bounds}} \qquad &\\
    d_M &= \delta v_{max} \lr{u_{max} - \frac{M_{f_{min}}}{V_{in_{max}}^2 C_{D_{max}}}} \approx 900
\end{align*}
Similarly, we have
\begin{table}[H]
    \centering
    \begin{tabular}{r l r r r}
        \hline \hline
        Parameter & Equation & Nominal & Minimum & Maximum\\ \hline \hline
        $\theta_1$ &
        $= \lr{\frac{J}{V_{in}^2 C_D}}$ &
        $3.7183e-1$ &
        $3.2388e-2$ &
        $2.3005$
        \\
        $\theta_2$ &
        $= \lr{\frac{b_m}{V_{in}^2 C_D}}$ &
        $0$ &
        $0$ &
        $1.0794$
        \\
        $\theta_3$ &
        $= \lr{\frac{1}{V_{in}^2}}$ &
        $4.1623e-3$ &
        $3.9062e-3$ &
        $4.4444e-3$
        \\
        \hline \hline
    \end{tabular}
    \caption{Parameter Bounds}
    \label{tab::parm_lims}
\end{table}
